Generating urban morphologies at large scales

### 2019-03-15 arxiv/v1/paper.tex
arxiv

\usepackage{subcaption}
\graphicspath{{figures/}}
% *****************
%  Requirements:
% *****************
%
% - All pages sized consistently at 8.5 x 11 inches (US letter size).
% - PDF length <= 8 pages for full papers, <=2 pages for extended
%    abstracts.
% - Abstract length <= 250 words.
% - No visible crop marks.
% - Images at no greater than 300 dpi, scaled at 100%.
% - Embedded open type fonts only.
% - All layers flattened.
% - No attachments.
% - All desired links active in the files.

@@

%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.2\textwidth}
        \includegraphics[width=\textwidth]{blocks}
        \caption{Blocks}
        \label{fig:blocks}
    \end{subfigure}
    \begin{subfigure}[b]{0.2\textwidth}
        \includegraphics[width=\textwidth]{expMixture}
        \caption{Kernel mixture}
        \label{fig:mixture}
    \end{subfigure}
    \begin{subfigure}[b]{0.2\textwidth}
        \includegraphics[width=\textwidth]{percolation}
        \caption{Network percolation}
        \label{fig:percolation}
    \end{subfigure}
    \begin{subfigure}[b]{0.2\textwidth}
        \includegraphics[width=\textwidth]{random}
        \caption{Random}
        \label{fig:random}
    \end{subfigure}
    \caption{Examples of patterns produced by the synthetic generators.}
    % TODO should provide parameters here
    \label{fig:generators}
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(2.767548582324828,42.12774259047379)}.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(2.956412030079216,48.95833438674378)}.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(2.8534915107882908,48.87943398394085)}.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(4.724576799597424,46.11247464316661)}.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(6.693161940127149,51.28067900621835)}.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(7.665417780766332,51.61719462734998)}.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(7.746400123854242,49.448716515580514)}.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(8.66720808445827,49.469125872820456)}.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(8.368921085687871,49.224787816959754)}.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(9.3988783289936,45.52643666558245)}.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(9.422039749719488,48.68506062982569)}.png}
    \end{subfigure}
    \begin{subfigure}[b]{0.1\textwidth}
        \includegraphics[width=\textwidth]{{osm_(10.529303821177011,57.458935658684915)}.png}
    \end{subfigure}
    \caption{Samples extracted from OpenStreetMap.}
    % provide coordinates ?
    \label{fig:osm}
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure*}
\vspace{-1cm}
  \centering
  \rotatebox{90}{Class 1}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/1/osm_2.43416877400257_48.5494220403648_1}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/1/osm_3.20479601880545_50.1572174642354_1}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/1/osm_6.03454192624923_43.1438923676911_1}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/1/osm_7.76412991205779_47.6437664789465_1}.png}}
  \end{subfigure}\\
  \rotatebox{90}{Class 2}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/2/osm_4.73115258198923_45.9763617017002_2}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/2/osm_4.92601740592234E-5_50.7945845258906_2}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/2/osm_8.76440233864255_50.3459471560717_2}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/2/osm_10.6351277289413_51.1689134935896_2}.png}}
  \end{subfigure}\\
  \rotatebox{90}{Class 3}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/3/osm_2.78910884212325_50.5481512216399_3}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/3/osm_20.0294237103859_51.5168560281418_3}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/3/osm_5.55350495469112_51.4926898192205_3}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/3/osm_23.8025598321731_54.950616933903_3}.png}}
  \end{subfigure}\\
  \rotatebox{90}{Class 4}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/4/osm_5.28978808584814_52.0605158929046_4}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/4/osm_6.11373040780706_50.9165373258647_4}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/4/osm_8.35334588815557_49.530653800312_4}.png}}
  \end{subfigure}
  \begin{subfigure}[b]{0.13\textwidth}
    \framebox{\includegraphics[width=\textwidth]{{osm/4/osm_12.4396942996003_50.983284784414_4}.png}}
  \end{subfigure}\\
  \caption{Typology applied to OpenStreetMap samples. The first class correspond mostly to a high density of linear buildings, recalling modern urbanism projects; the second disparate large buildings that can corresponds to industrials buildings in the outskirt of cities; the third disparate small buildings closer to periurban settlements; the fourth are denser and more complicated patterns evoking historical urban centers.}
  % provide coordinates ?
  \label{fig:osm_types}
\end{figure*}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure*}
\vspace{-1.8cm}
    \centering
    (1)
    \framebox{\includegraphics[width=0.18\linewidth]{closest1_blocks}}
    \framebox{\includegraphics[width=0.18\linewidth]{closest1_real}}\hspace{0.4cm}
    (2)
    \framebox{\includegraphics[width=0.18\linewidth]{closest2_expMixture}}
    \framebox{\includegraphics[width=0.18\linewidth]{closest2_real}}\\\vspace{0.2cm}
    (3)
    \framebox{\includegraphics[width=0.18\linewidth]{closest3_blocks}}
    \framebox{\includegraphics[width=0.18\linewidth]{closest3_real}}\hspace{0.4cm}
    (4)
    \framebox{\includegraphics[width=0.18\linewidth]{closest4_percolation}}
    \framebox{\includegraphics[width=0.18\linewidth]{closest4_real}}\\
    \includegraphics[width=\linewidth]{lhscalib_projrealpcs}
    \caption{Comparison of real morphologies with patterns produced by the synthetic generators. All points are projected into the first two components computed on the real measures only. Points in dark blue correspond to real configurations. The type of generator is given by the color in legend. Dark circle correspond to the centroids of clusters on which the calibration is done, their number giving the corresponding configurations shown above. For each, we successively show the best synthetic configuration ((1) block generator with $N_B=12,m_B=5,M_B=12$, (2) exponential mixture generator with $N_K=6,d_K=3.8,\theta_K=0.42$, (3) block generator with $N_B=11,m_B=1,M_B=14$, (4) percolation generator with $p_P=0.35,N_P=5,L_P=3.7$), and the real configuration from OSM beside each.}
    \label{fig:lhs}
\end{figure*}
%%%%%%%%%%%%%%

@@

\footnotesize
\bibliographystyle{apalike}
\bibliography{biblio} % replace by the name of your .bib file

>>>>

\usepackage{subcaption}
%\graphicspath{{figures/}}
% *****************
%  Requirements:
% *****************
%
% - All pages sized consistently at 8.5 x 11 inches (US letter size).
% - PDF length <= 8 pages for full papers, <=2 pages for extended
%    abstracts.
% - Abstract length <= 250 words.
% - No visible crop marks.
% - Images at no greater than 300 dpi, scaled at 100%.
% - Embedded open type fonts only.
% - All layers flattened.
% - No attachments.
% - All desired links active in the files.

@@

%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig1.png}
    \caption{Examples of patterns produced by the synthetic generators.}
    % TODO should provide parameters here
    \label{fig:generators}
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{fig2.png}
        \caption{Samples extracted from OpenStreetMap.}
    % provide coordinates ?
    \label{fig:osm}
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure*}
\vspace{-1cm}
  \centering
  \includegraphics[width=0.57\linewidth]{fig3}
    \caption{Typology applied to OpenStreetMap samples. The first class correspond mostly to a high density of linear buildings, recalling modern urbanism projects; the second disparate large buildings that can corresponds to industrials buildings in the outskirt of cities; the third disparate small buildings closer to periurban settlements; the fourth are denser and more complicated patterns evoking historical urban centers.}
  % provide coordinates ?
  \label{fig:osm_types}
\end{figure*}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%
\begin{figure*}
\vspace{-1.8cm}
    \centering
    \includegraphics[width=\linewidth]{fig4}
    \caption{Comparison of real morphologies with patterns produced by the synthetic generators. All points are projected into the first two components computed on the real measures only. Points in dark blue correspond to real configurations. The type of generator is given by the color in legend. Dark circle correspond to the centroids of clusters on which the calibration is done, their number giving the corresponding configurations shown above. For each, we successively show the best synthetic configuration ((1) block generator with $N_B=12,m_B=5,M_B=12$, (2) exponential mixture generator with $N_K=6,d_K=3.8,\theta_K=0.42$, (3) block generator with $N_B=11,m_B=1,M_B=14$, (4) percolation generator with $p_P=0.35,N_P=5,L_P=3.7$), and the real configuration from OSM beside each.}
    \label{fig:lhs}
\end{figure*}
%%%%%%%%%%%%%%

@@

\footnotesize
\begin{thebibliography}{}

\bibitem[Achibet et~al., 2014]{achibet2014model}
Achibet, M., Balev, S., Dutot, A., and Olivier, D. (2014).
\newblock A model of road network and buildings extension co-evolution.
\newblock {\em Procedia Computer Science}, 32:828--833.

\bibitem[Anas et~al., 1998]{anas1998urban}
Anas, A., Arnott, R., and Small, K.~A. (1998).
\newblock Urban spatial structure.
\newblock {\em Journal of economic literature}, 36(3):1426--1464.

\bibitem[Batty and Longley, 1987]{batty1987fractal}
Batty, M. and Longley, P.~A. (1987).
\newblock Fractal-based description of urban form.
\newblock {\em Environment and planning B: Planning and Design},
  14(2):123--134.

\bibitem[Boeing, 2018]{boeing2018measuring}
Boeing, G. (2018).
\newblock Measuring the complexity of urban form and design.
\newblock {\em URBAN DESIGN International}, 23(4):281--292.

\bibitem[Bonabeau, 1997]{bonabeau1997classical}
Bonabeau, E. (1997).
\newblock From classical models of morphogenesis to agent-based models of
  pattern formation.
\newblock {\em Artificial life}, 3(3):191--211.

\bibitem[Bretagnolle et~al., 2019]{bretagnolle2019following}
Bretagnolle, A., Guerois, M., and Pavard, A. (2019).
\newblock Following the population of european urban areas in the last half
  century (1961-2011): the tradeve database.
\newblock {\em Forthcoming in Cybergeo, European Journal of Geography}.

\bibitem[Ch{\'e}rel et~al., 2015]{10.1371/journal.pone.0138212}
Ch{\'e}rel, G., Cottineau, C., and Reuillon, R. (2015).
\newblock Beyond corroboration: Strengthening model validation by looking for
  unexpected patterns.
\newblock {\em PLoS ONE}, 10(9):e0138212.

\bibitem[Courtat et~al., 2011]{courtat2011mathematics}
Courtat, T., Gloaguen, C., and Douady, S. (2011).
\newblock Mathematics and morphogenesis of cities: A geometrical approach.
\newblock {\em Physical Review E}, 83(3):036106.

\bibitem[Cruz et~al., 2017]{cruz2017generation}
Cruz, C., Kirley, M., and Karakiewicz, J. (2017).
\newblock Generation and exploration of architectural form using a composite
  cellular automata.
\newblock In {\em Australasian Conference on Artificial Life and Computational
  Intelligence}, pages 99--110. Springer.

\bibitem[Epstein, 1999]{epstein1999agent}
Epstein, J.~M. (1999).
\newblock Agent-based computational models and generative social science.
\newblock {\em Complexity}, 4(5):41--60.

\bibitem[Fumega et~al., 2014]{fumega2014identification}
Fumega, J., Niza, S., and Ferr{\~a}o, P. (2014).
\newblock Identification of urban typologies through the use of urban form
  metrics for urban energy and climate change analysis.

\bibitem[Gauthier and Gilliland, 2006]{gauthier2006mapping}
Gauthier, P. and Gilliland, J. (2006).
\newblock Mapping urban morphology: a classification scheme for interpreting
  contributions to the study of urban form.
\newblock {\em Urban Morphology}, 10(1):41.

\bibitem[Herold et~al., 2003]{herold2003spatiotemporal}
Herold, M., Goldstein, N.~C., and Clarke, K.~C. (2003).
\newblock The spatiotemporal form of urban growth: measurement, analysis and
  modeling.
\newblock {\em Remote sensing of Environment}, 86(3):286--302.

\bibitem[Horner, 2007]{horner2007multi}
Horner, M.~W. (2007).
\newblock A multi-scale analysis of urban form and commuting change in a small
  metropolitan area (1990--2000).
\newblock {\em The Annals of Regional Science}, 41(2):315--332.

\bibitem[Kropf, 2009]{kropf2009aspects}
Kropf, K. (2009).
\newblock Aspects of urban form.
\newblock {\em Urban Morphology}, 13(2):105.

\bibitem[Le~N{\'e}chet, 2015]{le2015forme}
Le~N{\'e}chet, F. (2015).
\newblock De la forme urbaine {\`a} la structure m{\'e}tropolitaine: une
  typologie de la configuration interne des densit{\'e}s pour les principales
  m{\'e}tropoles europ{\'e}ennes de l’audit urbain.
\newblock {\em Cybergeo: European Journal of Geography}.

\bibitem[Liu et~al., 2017]{liu2017future}
Liu, X., Liang, X., Li, X., Xu, X., Ou, J., Chen, Y., Li, S., Wang, S., and
  Pei, F. (2017).
\newblock A future land use simulation model (flus) for simulating multiple
  land use scenarios by coupling human and natural effects.
\newblock {\em Landscape and Urban Planning}, 168:94--116.

\bibitem[Merrell et~al., 2010]{merrell2010computer}
Merrell, P., Schkufza, E., and Koltun, V. (2010).
\newblock Computer-generated residential building layouts.
\newblock In {\em ACM Transactions on Graphics (TOG)}, volume~29, page 181.
  ACM.

\bibitem[Mooney et~al., 2010]{mooney2010towards}
Mooney, P., Corcoran, P., and Winstanley, A.~C. (2010).
\newblock Towards quality metrics for openstreetmap.
\newblock In {\em Proceedings of the 18th SIGSPATIAL international conference
  on advances in geographic information systems}, pages 514--517. ACM.

\bibitem[{Moosavi}, 2017]{2017arXiv170902939M}
{Moosavi}, V. (2017).
\newblock {Urban morphology meets deep learning: Exploring urban forms in one
  million cities, town and villages across the planet}.
\newblock {\em arXiv e-prints}, page arXiv:1709.02939.

\bibitem[Moudon, 1997]{moudon1997urban}
Moudon, A.~V. (1997).
\newblock Urban morphology as an emerging interdisciplinary field.
\newblock {\em Urban morphology}, 1(1):3--10.

\bibitem[Newman and Kenworthy, 2000]{newman2000sustainable}
Newman, P. and Kenworthy, J. (2000).
\newblock Sustainable urban form: the big picture.
\newblock {\em Achieving sustainable urban form}, pages 109--120.

\bibitem[Parish and M\"{u}ller, 2001]{Parish:2001:PMC:383259.383292}
Parish, Y. I.~H. and M\"{u}ller, P. (2001).
\newblock Procedural modeling of cities.
\newblock In {\em Proceedings of the 28th Annual Conference on Computer
  Graphics and Interactive Techniques}, SIGGRAPH '01, pages 301--308, New York,
  NY, USA. ACM.

\bibitem[Pesaresi and Bianchin, 2003]{pesaresi2003recognizing}
Pesaresi, M. and Bianchin, A. (2003).
\newblock Recognizing settlement structure using mathematical morphology and
  image texture.
\newblock {\em Remote sensing and urban analysis: GISDATA}, 9:46--60.

\bibitem[Piou et~al., 2009]{piou2009proposing}
Piou, C., Berger, U., and Grimm, V. (2009).
\newblock Proposing an information criterion for individual-based models
  developed in a pattern-oriented modelling framework.
\newblock {\em Ecological Modelling}, 220(17):1957--1967.

\bibitem[Raimbault, 2018a]{raimbault2018calibration}
Raimbault, J. (2018a).
\newblock Calibration of a density-based model of urban morphogenesis.
\newblock {\em PloS one}, 13(9):e0203516.

\bibitem[Raimbault, 2018b]{raimbault2018multi}
Raimbault, J. (2018b).
\newblock Multi-modeling the morphogenesis of transportation networks.
\newblock In {\em Artificial Life Conference Proceedings}, pages 382--383. MIT
  Press.

\bibitem[Raimbault, 2018c]{raimbault2018urban}
Raimbault, J. (2018c).
\newblock An urban morphogenesis model capturing interactions between networks
  and territories.
\newblock In {\em Mathematics of Urban Morphogenesis, D'Acci L., ed. Springer
  Birkhauser Mathematics.}

\bibitem[Raimbault et~al., 2014]{raimbault2014hybrid}
Raimbault, J., Banos, A., and Doursat, R. (2014).
\newblock A hybrid network/grid model of urban morphogenesis and optimization.
\newblock In {\em 4th International Conference on Complex Systems and
  Applications}, pages 51--60.

\bibitem[Reuillon et~al., 2013]{reuillon2013openmole}
Reuillon, R., Leclaire, M., and Rey-Coyrehourcq, S. (2013).
\newblock Openmole, a workflow engine specifically tailored for the distributed
  exploration of simulation models.
\newblock {\em Future Generation Computer Systems}, 29(8):1981--1990.

\bibitem[Rode et~al., 2014]{rode2014cities}
Rode, P., Keim, C., Robazza, G., Viejo, P., and Schofield, J. (2014).
\newblock Cities and energy: urban morphology and residential heat-energy
  demand.
\newblock {\em Environment and Planning B: Planning and Design},
  41(1):138--162.

\bibitem[Schwarz, 2010]{Schwarz201029}
Schwarz, N. (2010).
\newblock Urban form revisited---selecting indicators for characterising
  european cities.
\newblock {\em Landscape and Urban Planning}, 96(1):29 -- 47.

\bibitem[Serra, 1983]{serra1983image}
Serra, J. (1983).
\newblock {\em Image analysis and mathematical morphology}.
\newblock Academic Press, Inc.

\bibitem[Watson et~al., 2008]{watson2008procedural}
Watson, B., M{\"u}ller, P., Veryovka, O., Fuller, A., Wonka, P., and Sexton, C.
  (2008).
\newblock Procedural urban modeling in practice.
\newblock {\em IEEE Computer Graphics and Applications}, 28(3):18--26.

\bibitem[Webster, 1995]{webster1995urban}
Webster, C. (1995).
\newblock Urban morphological fingerprints.
\newblock {\em Environment and Planning B: Planning and design},
  22(3):279--297.

\bibitem[Ye and Van~Nes, 2014]{ye2014quantitative}
Ye, Y. and Van~Nes, A. (2014).
\newblock Quantitative tools in urban morphology: Combining space syntax,
  spacematrix and mixed-use index in a gis framework.
\newblock {\em Urban morphology}, 18(2):97--118.

\end{thebibliography}
